### 2023-03-26 article3.qmd
finalize typo check

The biological carbon pump (BCP) refers to a series of processes that transport biogenic carbon produced in sunlit surface waters to the ocean interior [@Claustre2021-tx]. It is composed of three main pathways [@Claustre2021-tx; @Boyd2019-ez; @Siegel2022-wd]: the biological gravitational pump that is the gravitational settling of particulate organic carbon (POC); the physically mediated particle injection pump that represents physical mechanisms that transport both POC and dissolved organic carbon (DOC) to depth via mixing processes; and the biologically mediated particle injection pump that characterizes the transport of POC by diel and seasonal migration of animals in the water column. Historically, the BCP was mainly studied with sediment traps [@Honjo2008-kn] and Thorium-234 radionuclide disequilibria [@Buesseler2007-ql] focused on the gravitational pump hence the contribution of DOC and migrating animals to the BCP was poorly known. However, the advent of autonomous underwater vehicles (AUVs) equipped with a variety of physical and biogeochemical sensors have demonstrated their ability to better understand them [e.g. @Omand2015-mf; @DallOlmo2016-ex; @Llort2018-pa; @Lacour2019-id; @Haentjens2020-dc; @Stukel2017-lc]. Still, we are missing processes to close the carbon budget [@Giering2014-tj; @Boyd2019-ez] and unkowns remain in the under-sampled mesopelagic (i.e. twilight) zone [@Martin2020-wa]. In order to fill the observational gaps, the Biogeochemical-Argo (BGC-Argo) network aims to develop an operational global array of 1000 profiling floats measuring six core variables from the surface to 2000 m [@Claustre2020-jo]: oxygen, nitrate, pH, chlorophyll a (Chla), suspended particles and downwelling irradiance. In addition to the six core variables, new sensors have been developped to target specific BCP-related questions [@Claustre2020-jo; @Claustre2021-tx; @Chai2020-uq]. In this study, we will focus on BGC-Argo floats equipped with two additional sensors: the Underwater Vision Profiler (UVP6) [@Picheral2021-sx] and a transmissometer used as an optical sediment trap (OST).

The UVP6 is a portable version of the UVP5 [@Picheral2010-to], specifically designed for AUVs [@Picheral2021-sx]. It consists of an underwater camera that counts particles and images objects in, respectively, the 0.1 - 2.5 mm and 0.6 - 2.5 cm size range. In contrast with UVP5 deployments on cabled platforms, UVP6 deployed on long-term drifting AUVs (e.g. BGC-Argo floats) are rarely recovered. Therefore, the latest version of the UVP6 also embarks an embedded image classification algorithm that transmits the abundance of 20 classes (16 biological classes) in near-real time. The OST consists of a vertically mounted transmissometer whose upward-facing optical window intercepts sinking particles to estimate the downward POC flux. The latter have already been used on AUVs [@Bishop2004-at; @Bishop2009-ka; @Estapa2013-gw; @Estapa2017-jr; @Estapa2019-nk] and have demonstrated their usefulness to characterize the gravitational pump.

For the first time, BGC-Argo floats equipped with both the UVP6 and an OST were deployed in the Labrador Sea (LS) to investigate the seasonal and episodic dynamics of particles and carbon fluxes. The LS is a basin of the subpolar North Atlantic (NA) ocean which represents 20% of the global ocean carbon sink [@Takahashi2009-rv]. The efficiency of this sink is explained by both deep winter convection that traps CO$_{2}$ from the atmosphere [@Vage2008-qa; @Yashayaev2009-fe; @Yashayaev2017-mn] and by the largest spring phytoplankton bloom [@Siegel2002-hk] that consumes CO$_{2}$ for the photosynthetic production of organic matter. The triggering mechanism of the NA bloom was initially explained by the 'Critical Depth Hypothesis' of @Sverdrup1953-ki that defines a critical surface mixing depth where phytoplankton growth is equal to phytoplankton losses. According to @Sverdrup1953-ki, a bloom is therefore triggered when the surface mixed layer depth (MLD) is shallower than this critical depth resulting in a positive phytoplankton growth rate. However, this hypothesis was challenged by @Behrenfeld2010-my who suggested that the initiation of the NA blooms begins in winter with a slow phytoplankton biomass increase over the following months (i.e. 'Dilution-Recoupling' hypothesis). These hypotheses have been investigated with BGC-Argo floats but the debate still remains [@Mignot2018-gm; @Yang2020-hw; @Boss2010-do]. Distinct NA bloom phenologies were highlighted by @Lacour2015-da who used a climatology of satellite Chla to divide the NA into 6 bioregions. In their bioregionalization (see also their Figure 2), the LS is characterized by two bioregions with distinct bloom phenologies on both side of the 60°N parallel. The northern part is characterized by a short and potentially more intense spring bloom in late April whereas the bloom in the southern part starts in April-May and slowly develops to reach its maximum in June. @Lacour2015-da concluded that the concurrent influence of surface light and mixing was the first-order mechanism controlling the onset of the spring bloom in both bioregions. This is coherent with the results of @Wu2008-vw and @Frajka-Williams2010-ph who found that the early bloom in the northern part is due to a very shallow mixed layer associated with low-salinity waters (i.e. haline stratification) while the southern bloom is related to the development of the seasonal thermocline (i.e. thermal stratification due to increased solar radiation). In late May 2022, two pairs of BGC-Argo floats were deployed in the southern part of the LS at the time of the spring bloom. While BGC-Argo floats typically drift at 1000 m for 10 days between each ascending profile, all floats were configured to drift at three distinct parking depths (200 m, 500 m and 1000 m) to study the downward POC flux and its attenuation derived from beam attenuance [@Estapa2023-oz] and to study particle size distributions (PSD) and concentrations with the UVP6.

The goals of this study are threefold: 1) the comparison of the UVP6 and OST as two independent measurements of downward carbon fluxes and particle abundance on BGC-Argo floats; 2) the exploration of the seasonality (bloom and non-bloom periods) of downward POC fluxes and particle abundance in the LS; 3) the evaluation of the new drifting configuration and how it could be improved to study specific BCP-related questions.

@@

In order to compute $F_{small}$, we firstly computed the slope of each segment between jumps (positive and/or negative, see @fig-estapa-method_article). Any segment with less than 4 observations or a negative slope was removed assuming that either the so-called fit failed (leading to undetected jumps) either the transmissometer window was perturbed by factors other than the pump cleaning the optical window (e.g. turbulence or zooplankton consumption of accumulated material). Afterwards, we computed the weighted average slope ($slope_{w}$) of each segment to derive the small particles flux using the linear relationship between the beam attenuance flux and the POC flux (see first panel of Figure 2 in @Estapa2023-oz).

@@

Satellite Chla data were downloaded from a daily-merged cloud free GlobColour product (doi: 10.48670/moi-00281) with a spatial resolution of 4 km. Mixed layer depth (MLD) derived from satellite observations were downloaded from near-real time weekly data from the ARMOR3D product (doi: 10.48670/moi-00052) with a spatial resolution of 0.25°.

@@

Vertical profiles of particle concentrations in the lower (102 - 512 $\mu$m, see @fig-uvp6-profiling-102-406) and upper (0.512 - 2.5 mm, see @fig-uvp6-profiling-512-2500) size range of the UVP6 show similar patterns across all floats. In the lower part of the size range, @fig-uvp6-profiling-102-406 shows the rapid emptying of the water column in November. This process occurred on the entire water column (e.g. size class 406, float 4903634) but also started with more intensity from below the surface (e.g. size class 102, float 6904240). All floats also measured a local particle abundance maximum around 800 - 1000 m whose origin is analyzed in the Discussion. In the upper part of the size range, @fig-uvp6-profiling-512-2500 shows a rapid emptying of the entire water column starting in November. In contrast with small classes (referred to here as below 512 $\mu$m), some particles, especially above 1.5 mm, have almost entirely disappeared from the water column by September. However, the rapid increase and decrease of particles on the entire water column around July-August for floats 6904241 and 1902578 (still in the same zone at that time) could suggest an export event.

@@

$F_{large}$ was estimated at 200 m between 0 (no deposition of large particles on the transmissometer window) and `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$max_largef, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$mean_largef, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$std_largef, 1)` mg C m$^{-2}$ day$^{-1}$. High fluxes (\> 100 mg C m$^{-2}$ day$^{-1}$) were measured by 3 out of 4 floats at the end of May before a sharp decrease towards July. At 500 m, $F_{large}$ ranges between `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$min_largef, 1)` mg C m$^{-2}$ day$^{-1}$ and `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$max_largef, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$mean_largef, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$std_largef, 1)` mg C m$^{-2}$ day$^{-1}$, decreasing from September to February. At 1000 m, $F_{large}$ shows a similar pattern than the one observed for $F_{small}$ with an increase from June to mid-July, followed by a decrease towards March, with values ranging from 0 to `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$max_largef, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$mean_largef, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$std_largef, 1)` mg C m$^{-2}$ day$^{-1}$.

@@

Still, it is unclear why we observe a progressive emptying of the water column starting below 500 m for size classes below 323 $\mu$m (@fig-uvp6-profiling-102-406). This pattern could result from several causes. It could either be the signature of a subduction event [@Llort2018-pa] either the end of a slow sinking export (i.e latent dynamic of the system) or a sign of fragmentation processes by zooplankton (i.e. zooplankton feeding). Therefore, we looked at physical properties (density anomaly and spiciness) and well as particle characteristics (zooplankton concentration and spectral slope) to investigate this particularity (@fig-spice). Spiciness is a variable that allows the differentiation of water masses with distinct thermohaline properties but similar density [@Flament2002-zm]. @fig-spice shows that both the density and the spiciness fields are uniform below 500 m hence it is unlikely that a subduction event would be the reason for this decrease in particle abundance below 500 m. Using the embedded zooplankton classification results from the UVP6, we looked at concentrations of *Calanoida*, a species that is abundant in the NA [@Corkett1979-ha]. @fig-spice shows that the concentration of *Calanoida* is higher from the end of May to July in the surface layer. There also seems to be a lower patch between 250 and 500 m from August to November however it is difficult to estimate their impact on particle concentrations at this stage. Finally, we computed the spectral slope to look for aggregation/fragmentation processes. The spectral slope defines the slope of the PSD where a high (in absolute values) spectral slope indicates that small particules dominate the PSD. Here, the panel on spectral slopes in @fig-spice shows a lower (in absolute values) spectral slope at the beginning of the time series but it is also difficult to relate it to biological processes such as zooplankton feeding without any additional data.

@@

```{=latex}
\newpage
```
### Comparing OST and UVP data

@@

For the first time, BGC-Argo floats equipped with both an OST and the UVP6 have been deployed to better characterize the downward carbon flux and the nature of sinking particles from a multi-instrument approach [@Claustre2021-tx]. The quantification of the POC flux using the OST method [@Bishop2004-at; @Estapa2013-gw; @Estapa2017-jr; @Estapa2019-nk; @Estapa2023-oz] is based on an empirical POC:ATN ratio [@Estapa2023-oz] whereas UVP6 PSD measurements are used to compute POC fluxes using @eq-guidi-article3:

$$
F = \sum_{i}^{N}C_{i}Ad_{i}^{b}
$$ {#eq-guidi-article3}

where $C_{i}$, A and b represent, respectively, the concentration of particles (#/L) for the $i^{th}$ class of mean diameter $d_{i}$ (in mm) and 2 constants with $b$ being related to the fractal dimension ($D$) of an aggregate by $D = (b +1)/2$ [@Guidi2008-vp].

The use of @eq-guidi-article3 to derive carbon fluxes from PSD was firstly implemented by @Guidi2008-vp who used a minimization procedure between sediment traps data and estimated fluxes using PSD from several previous versions of the UVP to find the optimal value of $A$ and $b$ (i.e. 12.5 and 3.81). @Iversen2010-an and @Fender2019-ou followed the same procedure and concluded that the couple of parameters found by [@Guidi2008-vp] could not be used globally at the expense of greatly over- or underestimating POC fluxes, depending on the sampling region. In addition, the formulation of such a model implies that $A$ and $b$ would be valid at global scale, at all depths, for all UVP models and across all size classes which is arguable [@Bisson2022-bt]. @eq-guidi-article3 also assumes that the flux is only size-dependent though the main driver for the settling of aggregates is still debated [@Iversen2020-kb; @Iversen2023-qj]. As a result, the direct comparison of carbon fluxes derived from both OST and UVP data with @eq-guidi-article3 should be focused on the trend rather than on absolute carbon flux values.

```{r, compute guidi fluxes at parking depth, fig.height=6, fig.width=8}
#| label: fig-comparison-ost-uvp
#| fig-cap: Comparison of total carbon fluxes (F$_{small}$ + F$_{large}$) derived from the OST (black) and the UVP6 using the A and b values of @Guidi2008-vp (red) and @Iversen2010-an (yellow) in @eq-guidi-article3. OST data from float 6904241 stops in November due to a transmissometer failure.

@@

@fig-comparison-ost-uvp shows the comparison between the total carbon flux measured by the OST ($F_{total} = F_{small} + F_{large}$) and the UVP6 (median of all UVP measurements while the float was drifting) at all drifting depths. Overall, carbon fluxes estimated with the $A$ and $b$ coefficients of @Guidi2008-vp are lower than the ones measured by the OST whereas the same estimation using the coefficient of @Iversen2010-an generally overestimates the OST at 200 m but is of the same order at 500 m and 1000 m. Without additional measurements (e.g. co-deployed sediment traps), it is however impossible to decipher which measurement is closest to the truth. Nonetheless, carbon fluxes measured at 1000 m by the OST and the UVP6 with the coefficients of @Iversen2010-an are both well correlated (\> 0.6 for all floats) and of similar magnitudes while carbon fluxes using @Guidi2008-vp are one order of magnitude lower. In their paper, @Iversen2010-an proposed that the carbon fluxes discrepancy could be due to different biogeochemical regimes where the relationship of @Guidi2008-vp was rather based on sediment traps at open ocean sites with lower carbon fluxes [@Honjo2008-kn] while the study site of @Iversen2010-an was located in a highly productive system at the continental margin off Cape Blanc in Mauritania. The LS is productive during the spring bloom [@Lacour2015-da] therefore it is coherent to find a closer relationship with estimations based on a highly productive system.

@@

The current configuration of all floats in the LS was a 10-day ascending profile acquisition with drifting at 200 m for one day, 500 m for 3 days and 1000 m for 5 days. During drifting, OST measurements were taken every 30 minutes at all depths whereas UVP measurements were taken every 20 minutes at 200 m and every 2h at 500 m and 1000 m. This initial configuration was based on a compromise between science targets and energy consumption limitations for long-term deployment (years). However, I think this configuration could be adapted depending on the period of the year to target specific processes. For instance, I tried to evaluate sinking speeds from particle concentrations using a gaussian fit in different water layers to follow the gaussian peak with time and depth for each size class. I managed to compute realistic sinking speeds but the uncertainty was huge and potentially biased because I was just trying to fit something I saw in the data. Therefore, I did not use those estimations here but I think it would be possible to compute them if the float was sampling every day when the abundance of particles is at its maximum (e.g. during the spring bloom). Similarly, to address the question of the vertical migration, a 10-day temporal resolution is way to low because plankton images are rare compared to detritus so the sampling volume should be greatly increased to have a better estimation of the presence (or absence) of zooplankton. Finally, it would perhaps be interesting to increase the time spent at 200 m (to 3 days) and decrease the time spent at 1000 m to 3 days instead of 5) where the probability of capturing big particles is lower than at 200 m. There could also be UVP6 and OST measurements closer in time at all drifting depths to have a better comparison of attenuation slopes/jumps and biovolumes.

>>>>

The biological carbon pump (BCP) refers to a series of processes that transport biogenic carbon produced in sunlit surface waters to the ocean interior [@Claustre2021-tx]. It is composed of three main pathways [@Claustre2021-tx; @Boyd2019-ez; @Siegel2022-wd]: the biological gravitational pump that is the gravitational settling of particulate organic carbon (POC); the physically mediated particle injection pump that represents physical mechanisms that transport both POC and dissolved organic carbon (DOC) to depth via mixing processes; and the biologically mediated particle injection pump that characterizes the transport of POC by diel and seasonal migration of animals in the water column. Historically, the BCP was mainly studied with sediment traps [@Honjo2008-kn] and Thorium-234 radionuclide disequilibria [@Buesseler2007-ql] focused on the gravitational pump hence the contribution of DOC and migrating animals to the BCP was poorly known. However, the advent of autonomous underwater vehicles (AUVs) equipped with a variety of physical and biogeochemical sensors have demonstrated their ability to better understand them [e.g. @Omand2015-mf; @DallOlmo2016-ex; @Llort2018-pa; @Lacour2019-id; @Haentjens2020-dc; @Stukel2017-lc]. Still, we are missing processes to close the carbon budget [@Giering2014-tj; @Boyd2019-ez] and unknowns remain in the under-sampled mesopelagic (i.e. twilight) zone [@Martin2020-wa]. In order to fill the observational gaps, the Biogeochemical-Argo (BGC-Argo) network aims to develop an operational global array of 1000 profiling floats measuring six core variables from the surface to 2000 m [@Claustre2020-jo]: oxygen, nitrate, pH, chlorophyll a (Chla), suspended particles and downwelling irradiance. In addition to the six core variables, new sensors have been developed to target specific BCP-related questions [@Claustre2020-jo; @Claustre2021-tx; @Chai2020-uq]. In this study, we will focus on BGC-Argo floats equipped with two additional sensors: the Underwater Vision Profiler (UVP6) [@Picheral2021-sx] and a transmissometer used as an optical sediment trap (OST).

The UVP6 is a portable version of the UVP5 [@Picheral2010-to], specifically designed for AUVs [@Picheral2021-sx]. It consists of an underwater camera that counts particles and takes images of objects in, respectively, the 0.1 - 2.5 mm and 0.6 - 2.5 cm size range. In contrast with UVP5 deployments on cabled platforms, UVP6 deployed on long-term drifting AUVs (e.g. BGC-Argo floats) are rarely recovered. Therefore, the latest version of the UVP6 also embarks an embedded image classification algorithm that transmits the abundance of 20 classes (16 biological classes) in near-real time. The OST consists of a vertically mounted transmissometer whose upward-facing optical window intercepts sinking particles to estimate the downward POC flux. The latter have already been used on AUVs [@Bishop2004-at; @Bishop2009-ka; @Estapa2013-gw; @Estapa2017-jr; @Estapa2019-nk] and have demonstrated their usefulness to characterize the gravitational pump.

For the first time, BGC-Argo floats equipped with both the UVP6 and an OST were deployed in the Labrador Sea (LS) to investigate the seasonal and episodic dynamics of particles and carbon fluxes. The LS is a basin of the subpolar North Atlantic (NA) ocean which represents 20% of the global ocean carbon sink [@Takahashi2009-rv]. The efficiency of this sink is explained by both deep winter convection that traps CO$_{2}$ from the atmosphere [@Vage2008-qa; @Yashayaev2009-fe; @Yashayaev2017-mn] and by the largest spring phytoplankton bloom [@Siegel2002-hk] that consumes CO$_{2}$ for the photosynthetic production of organic matter. The triggering mechanism of the NA bloom was initially explained by the 'Critical Depth Hypothesis' of @Sverdrup1953-ki that defines a critical surface mixing depth where phytoplankton growth is equal to phytoplankton losses. According to @Sverdrup1953-ki, a bloom is therefore triggered when the surface mixed layer depth (MLD) is shallower than this critical depth resulting in a positive phytoplankton growth rate. However, this hypothesis was challenged by @Behrenfeld2010-my who suggested that the initiation of the NA bloom begins in winter with a slow phytoplankton biomass increase over the following months (i.e. 'Dilution-Recoupling' hypothesis). These hypotheses have been investigated with BGC-Argo floats but the debate still remains [@Mignot2018-gm; @Yang2020-hw; @Boss2010-do]. Distinct NA bloom phenologies were highlighted by @Lacour2015-da who used a climatology of satellite Chla to divide the NA into 6 bioregions. In their bioregionalization (see also their Figure 2), the LS is characterized by two bioregions with distinct bloom phenologies on both side of the 60°N parallel. The northern part is characterized by a short and potentially more intense spring bloom in late April whereas the bloom in the southern part starts in April-May and slowly develops to reach its maximum in June. @Lacour2015-da concluded that the concurrent influence of surface light and mixing was the first order mechanism controlling the onset of the spring bloom in both bioregions. This is coherent with the results of @Wu2008-vw and @Frajka-Williams2010-ph who found that the early bloom in the northern part is due to a very shallow mixed layer associated with low-salinity waters (i.e. haline stratification) while the southern bloom is related to the development of the seasonal thermocline (i.e. thermal stratification due to increased solar radiation). In late May 2022, two pairs of BGC-Argo floats were deployed in the southern part of the LS at the time of the spring bloom. While BGC-Argo floats typically drift at 1000 m for 10 days between each ascending profile, all floats were configured to drift at three distinct parking depths (200 m, 500 m and 1000 m) to study the downward POC flux and its attenuation derived from beam attenuance [@Estapa2023-oz] and to study particle size distributions (PSDs) and concentrations with the UVP6.

The goals of this study are threefold: 1) the comparison of the UVP6 and the OST as two independent measurements of downward carbon fluxes and particle abundance on BGC-Argo floats; 2) the exploration of the seasonality (bloom and non-bloom periods) of downward POC fluxes and particle abundance in the LS; 3) the evaluation of the new drifting configuration and how it could be improved to study specific BCP-related questions.

@@

In order to compute $F_{small}$, we firstly computed the slope of each segment between jumps (positive and/or negative, see @fig-estapa-method_article). Any segment with less than 4 observations or a negative slope was removed assuming that either the so-called fit failed (leading to undetected jumps) either the transmissometer window was perturbed by factors other than the pump cleaning the optical window (e.g. turbulence or zooplankton consumption of accumulated material). Afterwards, we computed the weighted average slope ($slope_{w}$) of each segment to derive the small particle flux using the linear relationship between the beam attenuance flux and the POC flux (see first panel of Figure 2 in @Estapa2023-oz).

@@

Satellite Chla data were downloaded from a daily-merged cloud free GlobColour product (doi: 10.48670/moi-00281) with a spatial resolution of 4 km. MLD derived from satellite observations were downloaded from near-real time weekly data from the ARMOR3D product (doi: 10.48670/moi-00052) with a spatial resolution of 0.25°.

@@

Vertical profiles of particle concentrations in the lower (102 - 512 $\mu$m, see @fig-uvp6-profiling-102-406) and upper (0.512 - 2.5 mm, see @fig-uvp6-profiling-512-2500) size range of the UVP6 show similar patterns across all floats. In the lower part of the size range, @fig-uvp6-profiling-102-406 shows the rapid emptying of the water column in November. This process occurred on the entire water column (e.g. size class 406, float 4903634) but also started with more intensity from below the surface (e.g. size class 102, float 6904240). All floats also measured a local particle abundance maximum around 800 - 1000 m whose origin is analyzed in the Discussion. In the upper part of the size range, @fig-uvp6-profiling-512-2500 shows a rapid emptying of the entire water column starting in November. In contrast with small classes (referred to here as below 512 $\mu$m), some particles, especially above 1.5 mm, have almost entirely disappeared from the water column by September. However, the rapid increase and decrease of particles on the entire water column around July-August for floats 6904241 and 1902578 (still in the same geographical zone at that time) could suggest an export event.

@@

$F_{large}$ was estimated at 200 m between 0 (no deposition of large particles on the transmissometer window) and `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$max_largef, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$mean_largef, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '200 m',]$std_largef, 1)` mg C m$^{-2}$ day$^{-1}$. High fluxes (\> 100 mg C m$^{-2}$ day$^{-1}$) were measured by 3 out of 4 floats at the end of May before a sharp decrease towards July. At 500 m, $F_{large}$ ranges between `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$min_largef, 1)` mg C m$^{-2}$ day$^{-1}$ and `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$max_largef, 1)` mg C m$^{-2}$ day$^{-1}$ with an average of `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$mean_largef, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '500 m',]$std_largef, 1)` mg C m$^{-2}$ day$^{-1}$, decreasing from September to February. At 1000 m, $F_{large}$ shows a similar pattern than the one observed for $F_{small}$ with an increase from June to mid-July, followed by a decrease towards March, with values ranging from 0 to `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$max_largef, 1)` mg C m$^{-2}$ day$^{-1}$ and an average of `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$mean_largef, 1)` $\pm$ `r round(cflux_info_table[cflux_info_table$park_depth == '1000 m',]$std_largef, 1)` mg C m$^{-2}$ day$^{-1}$.

@@

Still, it is unclear why we observe a progressive emptying of the water column starting below 500 m for size classes below 323 $\mu$m (@fig-uvp6-profiling-102-406). This pattern could result from several causes. It could either be the signature of a subduction event [@Llort2018-pa] either the end of a slow sinking export (i.e latent dynamics of the system) or a sign of fragmentation processes by zooplankton (i.e. zooplankton feeding). Therefore, we looked at physical properties (density anomaly and spiciness) and well as particle characteristics (zooplankton concentration and spectral slope) to investigate this particularity (@fig-spice). Spiciness is a variable that allows the differentiation of water masses with distinct thermohaline properties but similar density [@Flament2002-zm]. @fig-spice shows that both the density and the spiciness fields are uniform below 500 m hence it is unlikely that a subduction event would be the reason for this decrease in particle abundance below 500 m. Using the embedded zooplankton classification results from the UVP6, we looked at concentrations of *Calanoida*, a species that is abundant in the NA [@Corkett1979-ha]. @fig-spice shows that the concentration of *Calanoida* is higher from the end of May to July in the surface layer. There also seems to be a lower patch between 250 and 500 m from August to November however it is difficult to estimate their impact on particle concentrations at this stage. Finally, we computed the spectral slope to look for aggregation/fragmentation processes. The spectral slope defines the slope of the PSD where a high (in absolute values) spectral slope indicates that small particules dominate the PSD. Here, the panel on spectral slopes in @fig-spice shows a lower (in absolute values) spectral slope at the beginning of the time series but it is also difficult to relate it to biological processes such as zooplankton feeding without any additional data.

@@

```{=latex}
\newpage
```
### Comparing OST and UVP6 data

@@

For the first time, BGC-Argo floats equipped with both an OST and the UVP6 have been deployed to better characterize the downward carbon flux and the nature of sinking particles from a multi-instruments approach [@Claustre2021-tx]. The quantification of the POC flux using the OST method [@Bishop2004-at; @Estapa2013-gw; @Estapa2017-jr; @Estapa2019-nk; @Estapa2023-oz] is based on an empirical POC:ATN ratio [@Estapa2023-oz] whereas UVP6 PSD measurements are used to compute POC fluxes using @eq-guidi-article3:

$$
F = \sum_{i}^{N}C_{i}Ad_{i}^{B}
$$ {#eq-guidi-article3}

where $C_{i}$, A and B represent, respectively, the concentration of particles (#/L) for the $i^{th}$ class of mean diameter $d_{i}$ (in mm) and 2 constants with $B$ being related to the fractal dimension ($D$) of an aggregate by $D = (B +1)/2$ [@Guidi2008-vp].

The use of @eq-guidi-article3 to derive carbon fluxes from PSD was firstly implemented by @Guidi2008-vp who used a minimization procedure between sediment traps data and estimated fluxes using PSD from several previous versions of the UVP to find the optimal value of $A$ and $B$ (i.e. 12.5 and 3.81). @Iversen2010-an and @Fender2019-ou followed the same procedure and concluded that the couple of parameters found by [@Guidi2008-vp] could not be used globally at the expense of greatly over- or underestimating POC fluxes, depending on the sampling region. In addition, the formulation of such a model implies that $A$ and $B$ would be valid at global scale, at all depths, for all UVP models and across all size classes which is arguable [@Bisson2022-bt]. @eq-guidi-article3 also assumes that the flux is only size-dependent though the main driver for the settling of aggregates is still debated [@Iversen2020-kb; @Iversen2023-qj]. As a result, the direct comparison of carbon fluxes derived from both OST and UVP data with @eq-guidi-article3 should be focused on the trend rather than on absolute carbon flux values.

```{r, compute guidi fluxes at parking depth, fig.height=6, fig.width=8}
#| label: fig-comparison-ost-uvp
#| fig-cap: Comparison of total carbon fluxes (F$_{small}$ + F$_{large}$) derived from the OST (black) and the UVP6 using the $A$ and $B$ values of @Guidi2008-vp (red) and @Iversen2010-an (yellow) in @eq-guidi-article3. OST data from float 6904241 stops in November due to a transmissometer failure.

@@

@fig-comparison-ost-uvp shows the comparison between the total carbon flux measured by the OST ($F_{total} = F_{small} + F_{large}$) and the UVP6 (median of all UVP measurements while the float was drifting) at all drifting depths. Overall, carbon fluxes estimated with the $A$ and $B$ coefficients of @Guidi2008-vp are lower than the ones measured by the OST whereas the same estimation using the coefficient of @Iversen2010-an generally overestimates the OST at 200 m but is of the same order at 500 m and 1000 m. Without additional measurements (e.g. co-deployed sediment traps), it is however impossible to decipher which measurement is closest to the truth. Nonetheless, carbon fluxes measured at 1000 m by the OST and the UVP6 with the coefficients of @Iversen2010-an are both well correlated (\> 0.6 for all floats) and of similar magnitudes while carbon fluxes using @Guidi2008-vp are one order of magnitude lower. In their paper, @Iversen2010-an proposed that the carbon fluxes discrepancy could be due to different biogeochemical regimes where the relationship of @Guidi2008-vp was rather based on sediment traps at open ocean sites with lower carbon fluxes [@Honjo2008-kn] while the study site of @Iversen2010-an was located in a highly productive system at the continental margin off Cape Blanc in Mauritania. The LS is productive during the spring bloom [@Lacour2015-da] therefore it is coherent to find a closer relationship with estimations based on a highly productive system.

@@

The current configuration of all floats in the LS was a 10-day ascending profile acquisition with drifting at 200 m for one day, 500 m for 3 days and 1000 m for 5 days. During drifting, OST measurements were taken every 30 minutes at all depths whereas UVP measurements were taken every 20 minutes at 200 m and every 2h at 500 m and 1000 m. This initial configuration was based on a compromise between science targets and energy consumption limitations for long-term deployment (years). However, I think this configuration could be adapted depending on the period of the year to target specific processes. For instance, I tried to evaluate sinking speeds from particle concentrations using a gaussian fit in different water layers to follow the gaussian peak with time and depth for each size class. I managed to compute realistic sinking speeds but the uncertainty was huge and potentially biased because I was just trying to fit something I saw in the data. Therefore, I did not use those estimations here but I think it would be possible to compute them if the float was sampling every day when the abundance of particles is at its maximum (e.g. during the spring bloom). Similarly, to address the question of the vertical migration, a 10-day temporal resolution is way to low because plankton images are rare compared to detritus so the sampling volume should be greatly increased to have a better estimation of the presence (or absence) of zooplankton. Finally, it would perhaps be interesting to increase the time spent at 200 m (to 3 days) and decrease the time spent at 1000 m (to 3 days instead of 5) where the probability of capturing big particles is lower than at 200 m. There could also be UVP6 and OST measurements closer in time at all drifting depths to have a better comparison of attenuation slopes/jumps and biovolumes.

### 2023-03-26 bcp_sequestration.qmd
update
finalize typo check

# Revisiting the BCP with the CONVERSE framework {#bcp-sequestration}

@@

Why revise one pump when you can revise them all? 1 year and a half later, hundreds of emails, one promotion to first author, one negative review and one strong rebuttal, we are still on the road to publication. Here below is the revised version of our paper submitted in Nature Geoscience about the reassessment of the global sequestration (\> 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.

>>>>

# Revisiting the BCP with the CONVERSE framework {#sec-bcp-sequestration}

@@

Why revise one pump when you can revise them all? 1 year and a half later, hundreds of emails, one promotion to first author, one negative review and one strong rebuttal, we are still on the road to publication. Here below is the revised version of our paper submitted in Nature Geoscience about the reassessment of the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.
